Energy and exergy analysis of a cruise ship

### 2018-06-20 Manuscript/Manuscript.tex
Figures updates

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
%% Tthe amsmath package provides the "align" environment for nicer equation formatting
\usepackage{amsmath}
%% The package tabls helps in having nicer tables with higher spaces
\usepackage{tabls}
%% The package multirow allows merging together multiple cells vertifcally
\usepackage{multirow}
%% The package subcaption is for helping when using subfigures and their captions
\usepackage{subcaption}
%% This package is used for having nicer tables
\usepackage{booktabs}
% Package for improving table handling
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
% Package for drawing pictures
\usepackage{tikz}

@@

The case study ship is not provided with any means to directly measure the heat demand (e.g. steam flow meters), and it was hence necessary to provide estimations based on other measurements and assumptions. The heat demand is subdivided among the contributions of the HVAC preheater and reheater ($\dot{Q}_{HVAC,PH}$ and $\dot{Q}_{HVAC,RH}$), the hot water heater ($\dot{Q}_{HWH}$), the HFO heaters ($\dot{Q}_{HH}$) the tank heating systems for HFO and other liquids ($\dot{Q}_{HTH}$ and $\dot{Q}_{TH}$), the machinery space heating ($\dot{Q}_{MSH}$) and other tanks ($\dot{Q}_{OT}$). The heat generation is instead composed of the contribution of the exhaust gas boilers ($\dot{Q}_{EGB,ME,i}$ and $\dot{Q}_{EGB,AE,i}$), the heat recovery from the high temperature cooling systems ($\dot{Q}_{HTHR,j,i}$) and the boilers ($\dot{Q}_{AB}$).
 The heat demand and generation are summarized in equations \ref{eq:Qgen} and \ref{eq:Qdem}.
\begin{align}
\dot{Q}_{gen} & = \sum_{i=2,3} \dot{Q}_{EGB,ME,i} +  \sum_{i=1:4} \dot{Q}_{EGB,AE,i} + \sum_{j=ME,AE, i=1:4}\dot{Q}_{HTHR,j,i} + \dot{Q}_{AB} \label{eq:Qgen} \\
\dot{Q}_{dem} & = \dot{Q}_{HVAC,PH} + \dot{Q}_{HVAC,RH} + \dot{Q}_{HWH} + \dot{Q}_{HH} + \dot{Q}_{TH} + \dot{Q}_{G} + \dot{Q}_{OT} + 	\dot{Q}_{HTH} + \dot{Q}_{MSH} \label{eq:Qdem} \\
\end{align}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.95\linewidth]{Figures/segmentation_power_heat.png}
	\caption{Power (left) and heat (right) profiles, original (dotted) and segmented (full), for the 5 typical days and duration curves.}
	\label{fig:res:powerProfileSegmented}
\end{figure}

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
%% Tthe amsmath package provides the "align" environment for nicer equation formatting
\usepackage{amsmath}
%% The package tabls helps in having nicer tables with higher spaces
\usepackage{tabls}
%% The package multirow allows merging together multiple cells vertifcally
\usepackage{multirow}
%% The package subcaption is for helping when using subfigures and their captions
\usepackage{subcaption}
%% This package is used for having nicer tables
\usepackage{booktabs}
% Package for improving table handling
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
% Package for drawing pictures
\usepackage{tikz}
\usepackage{pgfplots}

@@

The case study ship is not provided with any means to directly measure the heat demand (e.g. steam flow meters), and it was hence necessary to provide estimations based on other measurements and assumptions. The heat demand is subdivided among the contributions of the HVAC preheater and reheater ($\dot{Q}_{HVAC,PH}$ and $\dot{Q}_{HVAC,RH}$), the hot water heater ($\dot{Q}_{HWH}$), the HFO heaters ($\dot{Q}_{HH}$) the tank heating systems for HFO and other liquids ($\dot{Q}_{HTH}$ and $\dot{Q}_{TH}$), the machinery space heating ($\dot{Q}_{MSH}$) and other tanks ($\dot{Q}_{OT}$). The heat generation is instead composed of the contribution of the exhaust gas boilers ($\dot{Q}_{EGB,ME,i}$ and $\dot{Q}_{EGB,AE,i}$), the heat recovery from the high temperature cooling systems ($\dot{Q}_{HTHR,j,i}$) and the boilers ($\dot{Q}_{AB}$).
 The heat demand and generation are summarized in equations \ref{eq:Qgen} and \ref{eq:Qdem}.
\begin{align}
\dot{Q}_{gen} & = \sum_{i=2,3} \dot{Q}_{EGB,ME,i} +  \sum_{i=1:4} \dot{Q}_{EGB,AE,i} + \sum_{j=ME,AE, i=1:4}\dot{Q}_{HTHR,j,i} + \dot{Q}_{AB} \label{eq:Qgen} \\
\dot{Q}_{dem} & = \dot{Q}_{HVAC,PH} + \dot{Q}_{HVAC,RH} + \dot{Q}_{HWH} + \dot{Q}_{HH} + \dot{Q}_{TH} + \dot{Q}_{G} + \dot{Q}_{OT} + 	\dot{Q}_{HTH} + \dot{Q}_{MSH} \label{eq:Qdem}
\end{align}

@@

\begin{figure}[htbp!]
	\centering
 	% \includegraphics[width=0.95\linewidth]{Figures/segmentation_power_heat.png}
 	\includegraphics[width=0.95\linewidth]{Figures/segmentation_new.pdf}
	\caption{Power (left) and heat (right) profiles, original (dotted) and segmented (full), for the 5 typical days and duration curves.}
	\label{fig:res:powerProfileSegmented}
\end{figure}
